New Metrics for Assessing Projection Pursuit Indexes, and Guiding Optimisation Choices

### 2024-09-18 jso.qmd
update diagram

Smoothness and squintability are computed following the procedures
outlined in @sec-smoothness and @sec-squintability and as illustrated in
@fig-smoothness and @fig-squintability. To compute smoothness, 300 random
bases are simulated. Index values and
projection distance (to the optimal basis) are calculated for each
random basis before fitting the Gaussian process model to obtain the
smoothness measure for the index.

@@

```{r}
#| label: fig-smoothness
#| out.width: 100%
#| fig.cap: "Illustration of steps to calculate smoothness. For a given projection pursuit problem defined by the shape to find, data dimension and the index function, 1) sample random bases given the orthonormality contraint, 2) calculate the projection distance and the index value for each random basis, and 3) fit a Gaussian process model of index values against projection distances to obtain the smoothness measure. "
# basis_smoothness <- sample_bases(idx = "splines2d", n_basis = 1000)
# basis_smoothness |>
#    ggplot(aes(x = dist, y = index)) +
#    geom_point() + 
#    labs(x = "Projection distance", y = "Index value") + 
#    theme_bw() +   
#   theme(axis.text = element_text(size = 20), axis.title = element_text(size = 30))
knitr::include_graphics(here::here("figures", "smoothness.png"))
```

>>>>

Smoothness and squintability are computed following the procedures
outlined in @sec-smoothness and @sec-squintability and as illustrated in
@fig-smoothness and @fig-squintability. To compute smoothness, 500 random
bases are simulated. Index values are calculated for each
random basis before fitting the Gaussian process model to obtain the
smoothness measure for the index.

@@

```{r}
#| label: fig-smoothness
#| out.width: 100%
#| fig.cap: "Illustration of steps to calculate smoothness. For a given projection pursuit problem defined by the shape to find, data dimension and the index function, 1) sample random bases given the orthonormality contraint and calculate the index value associated with each random basis, and 2) fit a Gaussian process model of index values against projection distances to obtain the smoothness measure. "
# basis_smoothness <- sample_bases(idx = "splines2d", n_basis = 1000)
# basis_smoothness |>
#    ggplot(aes(x = dist, y = index)) +
#    geom_point() + 
#    labs(x = "Projection distance", y = "Index value") + 
#    theme_bw() +   
#   theme(axis.text = element_text(size = 20), axis.title = element_text(size = 30))
knitr::include_graphics(here::here("figures", "smoothness.png"))
```

### 2024-09-18 jso.tex
update diagram

\begin{tcolorbox}[enhanced jigsaw, toptitle=1mm, rightrule=.15mm, arc=.35mm, colback=white, opacitybacktitle=0.6, colbacktitle=quarto-callout-note-color!10!white, toprule=.15mm, leftrule=.75mm, breakable, bottomrule=.15mm, colframe=quarto-callout-note-color-frame, opacityback=0, left=2mm, titlerule=0mm, title={Algorithm: Jellyfish Optimizer Pseudo Code}, bottomtitle=1mm, coltitle=black]

@@

Smoothness and squintability are computed following the procedures
outlined in Section~\ref{sec-smoothness} and
Section~\ref{sec-squintability} and as illustrated in
Figure~\ref{fig-smoothness} and Figure~\ref{fig-squintability}. To
compute smoothness, 300 random bases are simulated. Index values and
projection distance (to the optimal basis) are calculated for each
random basis before fitting the Gaussian process model to obtain the
smoothness measure for the index.

@@

\caption{\label{fig-smoothness}Illustration of steps to calculate
smoothness. For a given projection pursuit problem defined by the shape
to find, data dimension and the index function, 1) sample random bases
given the orthonormality contraint, 2) calculate the projection distance
and the index value for each random basis, and 3) fit a Gaussian process
model of index values against projection distances to obtain the
smoothness measure.}

>>>>

\begin{tcolorbox}[enhanced jigsaw, toprule=.15mm, bottomtitle=1mm, opacityback=0, left=2mm, toptitle=1mm, opacitybacktitle=0.6, colframe=quarto-callout-note-color-frame, title={Algorithm: Jellyfish Optimizer Pseudo Code}, rightrule=.15mm, coltitle=black, titlerule=0mm, breakable, arc=.35mm, colback=white, bottomrule=.15mm, leftrule=.75mm, colbacktitle=quarto-callout-note-color!10!white]

@@

Smoothness and squintability are computed following the procedures
outlined in Section~\ref{sec-smoothness} and
Section~\ref{sec-squintability} and as illustrated in
Figure~\ref{fig-smoothness} and Figure~\ref{fig-squintability}. To
compute smoothness, 500 random bases are simulated. Index values are
calculated for each random basis before fitting the Gaussian process
model to obtain the smoothness measure for the index.

@@

\caption{\label{fig-smoothness}Illustration of steps to calculate
smoothness. For a given projection pursuit problem defined by the shape
to find, data dimension and the index function, 1) sample random bases
given the orthonormality contraint and calculate the index value
associated with each random basis, and 2) fit a Gaussian process model
of index values against projection distances to obtain the smoothness
measure.}
